Assessment and optimization of respiratory syncytial virus prophylaxis regimens in Connecticut, \Sexpr{formatYear(startDate)}-\Sexpr{formatYear(endDate)}

### 2019-03-28 Paper/RSVOptimization.rnw
Transposed onset-offset plots
Tweaks

% TODO make 1-week rounding primary analysis
% TODO DPH acknowledgement
% TODO transpose onset-offset plots

@@

% TODO cite DW/VP paper re spatial variability

@@

Our goal was to construct a model of annual RSV incidence that allowed us to estimate characteristics of RSV seasons, such as season onset, season offset, and preventable fraction of a prophylaxis regimen. To that end, we fit smooth curves through annual RSV hospitalization data, and used resampling to obtain confidence intervals. This was performed using the ??? package in R (See ??? for details on the analytical method and R package.)

@@

%TODO citation needed

@@

In addition to 1-week rounding of our alternative prophylaxis schedules, we calculated 2- and 4-week rounding, to assess the impact of calendrical rounding on prophylaxis performance. (Supplemental methods \ref{smethod:rounding}.)

To analyze the effects of year-to-year variation between RSV seasons, we performed similar analysis, but with prophylaxis start in a given year being determined by the RSV timing of three prior years, rather than all years. (Supplemental methods \ref{smethod:seasonDrift} and \ref{smethod:temporalAdjustment}.)

@@

\subsection{Without calendrical rounding, spatially adjusted regimens are superior to the AAP recommendations}

@@

The six spatially-adjusted prophylaxis regimens (with no rounding of prophylaxis dates), yield results in all counties that are as good or better than the AAP guidelines. (Figure \ref{fig:coverageByRegionRegimen}). Statewide, the AAP guidelines offer protection to \Sexpr{regionStrategyCoverage("all", "aap", 0)} cases (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}). The alternative regimen based on statewide onset yields the smallest increase, to \Sexpr{regionStrategyCoverage("all", "stateOnset", 0)} (\Sexpr{regionStrategyCoverageCI("all", "stateOnset", 0, level)}); other alternative regimens yield similar results. Most of the increase comes from Hartford county, where the AAP guidelines protect \Sexpr{regionStrategyCoverage("Hartford", "aap", 0)} of cases (\Sexpr{regionStrategyCoverageCI("Hartford", "aap", 0, level)}), whereas the alternative regimen based on county-level offset generates the smallest increase, to \Sexpr{regionStrategyCoverage("Hartford", "countyOffset", 0)} (\Sexpr{regionStrategyCoverageCI("Hartford", "countyOnset", 0, level)}); other alternative regimens are comparable. In every county, all alternative regimens are non-inferior to the AAP guidelines and non-superior to each other.

@@

We also applied biweekly and monthly rounding to the start and end dates of our six alternative immunoprophylaxis regimens, and found that doing so diminished or erased the benefits. (Supplemental result \ref{sresult:rounding}). Finally, we analyzed long-term trends in the RSV season onset and offset and found that the season onset may be moving earlier (Supplemental result \ref{sresult:seasonDrift}), but that accounting for that drift did not yield a significant further increase in preventable RSV cases (Supplemental result \ref{sresult:temporalAdjustment}).

@@

Our effort to optimize timing of the prophylaxis regimen (without changing its duration, and therefore its pharmaceutical cost) shows a theoretical 1-2\% statewide decrease in RSV-associated hospitalizations among high-risk infants each year, primarily in counties with higher RSV burden (Fairfield, Hartford, and New Haven counties). The magnitude of that improvement declines after accounting for practicalities of clinical practice guideline implementation. Nonetheless, with clinical practice guidelines localized at the county level, and the timing of prophylaxis adjusted in each county by less than a whole month from the current AAP guidelines, we still found the potential for $\sim$1\% statewide decrease in RSV-associated hospitalizations among high risk infants. The prophylaxis regimen with which we were able to attain this improvement is the one in which prophylaxis in each county is timed relative to the midpoint of the RSV season (rounded to two weeks) in that county, which simultaneously reduces unprotected cases early in the season and ineffective prophylaxis late in the season. Increasing complexity of practice guidelines would carry with it increased cost of implementation (such as training of clinicians and other healthcare workers); it is therefore not apparent from our research alone that the potential benefits would outweigh the costs.

@@

The use of data aggregated by epidemiological weeks created a challenge for both our analysis and the interpretation of our results. In practice, clinical guidelines are typically expressed in terms of calendar weeks or months; as a result, our analysis contains errors of up to $\pm 0.5$ weeks when applied to the more natural calendar boundaries. Ideally, our analysis should be repeated with daily case counts aggregated into weeks and months that match week and month boundaries used in clinical guidelines.

>>>>

% TODO make 1-week rounding primary analysis
% TODO DPH acknowledgement
% TODO better month labels in onset-offset plots

@@

@@

Our goal was to construct a model of annual RSV incidence that allowed us to estimate characteristics of RSV seasons, such as season onset, season offset, and preventable fraction of a prophylaxis regimen. To that end, we fit smooth curves through annual RSV hospitalization data, and used resampling to obtain confidence intervals. This was performed using the \texttt{outbreak-inference} package in R, which we developed for this purpose. (See ??? for details on the analytical method and the R package.)

@@

%TODO citation needed re small subgroup

@@

In addition to the 1-week rounding of our alternative prophylaxis schedules, we also calculated schedules using 2- and 4-week rounding, to assess the impact of calendrical rounding on prophylaxis performance. (Supplemental methods \ref{smethod:rounding}.)

To analyze the effects of year-to-year variation between RSV seasons, we performed similar analysis, but with prophylaxis start in a given year being determined by the RSV season timing of the preceding three years, rather than all years. (Supplemental methods \ref{smethod:seasonDrift} and \ref{smethod:temporalAdjustment}.)

@@

\subsection{Spatially adjusted regimens are superior to the AAP recommendations}

@@

% TODO Update results to 1-week rounding

The six spatially-adjusted prophylaxis regimens, yield results in all counties that are as good or better than the AAP guidelines. (Figure \ref{fig:coverageByRegionRegimen}). Statewide, the AAP guidelines offer protection to \Sexpr{regionStrategyCoverage("all", "aap", 0)} cases (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}). The alternative regimen based on statewide onset yields the smallest increase, to \Sexpr{regionStrategyCoverage("all", "stateOnset", 0)} (\Sexpr{regionStrategyCoverageCI("all", "stateOnset", 0, level)}); other alternative regimens yield similar results. Most of the increase comes from Hartford county, where the AAP guidelines protect \Sexpr{regionStrategyCoverage("Hartford", "aap", 0)} of cases (\Sexpr{regionStrategyCoverageCI("Hartford", "aap", 0, level)}), whereas the alternative regimen based on county-level offset generates the smallest increase, to \Sexpr{regionStrategyCoverage("Hartford", "countyOffset", 0)} (\Sexpr{regionStrategyCoverageCI("Hartford", "countyOnset", 0, level)}); other alternative regimens are comparable. In every county, all alternative regimens are non-inferior to the AAP guidelines and non-superior to each other.

@@

We also applied 2-week and 4-week rounding to the start and end dates of our six alternative immunoprophylaxis regimens, and found that doing so diminished or erased the potential benefits. (Supplemental result \ref{sresult:rounding}). Finally, we analyzed long-term trends in the RSV season onset and offset and found that the season onset may be moving earlier (Supplemental result \ref{sresult:seasonDrift}), but that accounting for that drift did not yield a significant further increase in preventable RSV cases (Supplemental result \ref{sresult:temporalAdjustment}).

@@

Our effort to optimize timing of the prophylaxis regimen (without changing its duration, and therefore its pharmaceutical cost) shows a potential $\sim1\%$ statewide decrease in RSV-associated hospitalizations among high-risk infants each year, primarily in counties with higher RSV burden (Fairfield, Hartford, and New Haven counties), by using clinical practice guidelines localized at the county level, and with the timing of prophylaxis adjusted in each county by less than a whole month from the current AAP guidelines. The prophylaxis regimen with which we were able to attain this improvement is the one in which prophylaxis in each county is timed relative to the midpoint of the RSV season in that county, which simultaneously reduces unprotected cases early in the season and ineffective prophylaxis late in the season. Increasing complexity of practice guidelines would carry with it increased cost of implementation (such as training of clinicians and other healthcare workers); it is therefore not apparent from our research alone that the potential benefits would outweigh the costs.

@@

The use of data aggregated by epidemiological weeks created a challenge for both our analysis and the interpretation of our results. In practice, clinical guidelines are typically expressed in terms of calendar weeks or months; as a result, our analysis contains errors of up to $\pm 0.5$ weeks when applied to the more natural calendar boundaries of clinical guidelines. Ideally, our analysis should be repeated with daily case counts aggregated into weeks and months that match week and month boundaries used in clinical guidelines.
